Beliefs about meritocracy and non-meritocracy in international comparison

### 2020-08-19 docs/paper.Rmd
update

---
title: "Beliefs about meritocracy and non-meritocracy in international comparison"
css: "../input/css/custom.css"
linestretch: '1.5'
link-citations: yes
output:
  html_document:
    theme: flatly
    number_sections: true
    always_allow_html: yes
#  pdf_document:
#    keep_tex: false
#    template: null
#    number_sections: true
linkcolor: blue
bibliography:
  - ../input/bib/EconomiaMoral.bib
  - ../input/bib/meritocracy.bib
editor_options:
  chunk_output_type: console

---

>>>>

---
title: "Beliefs about meritocracy and non-meritocracy in international comparison"
css: "../input/css/custom.css"
linestretch: '1.5'
link-citations: yes
output:
  html_document:
    theme: flatly
    number_sections: true
    always_allow_html: yes
#  pdf_document:
#    keep_tex: false
#    template: null
#    number_sections: true
linkcolor: blue
bibliography:
  - ../input/bib/EconomiaMoral.bib
  - ../input/bib/meritocracy.bib
editor_options:
  chunk_output_type: console
---
